Deciding Bitvector Termination with Program Synthesis

### 2014-07-05 papers/termination/paper.tex
Extend data flow diagram
L language

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{pifont}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{pgf}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}
\usepackage{multicol}
\usepackage{appendix}
\usepackage{caption,subcaption}
\DeclareCaptionType{copyrightbox}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{framed}
\usepackage{tikz}
\usetikzlibrary{arrows, automata, shapes}

@@

Since termination for bitvector programs is known to be PSPACE-complete~\cite{DBLP:conf/tacas/CookKRW10} it
is perhaps unsurprising that we are able to decide it.  We will now show that our time complexity is
asymptotically a function of the Kolmogorov complexity of the (non-)termination proof, and argue heuristically
that this gives our procedure various desirable qualities.

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{pifont}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{pgf}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}
\usepackage{multicol}
\usepackage{appendix}
\usepackage{caption,subcaption}
\DeclareCaptionType{copyrightbox}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{framed}
\usepackage{tikz}
\usetikzlibrary{arrows, automata, shapes, calc}

@@

Since termination for bitvector programs is known to be PSPACE-complete \cite{DBLP:conf/tacas/CookKRW10} it
is perhaps unsurprising that we are able to decide it.  We will now show that our time complexity is
asymptotically a function of the Kolmogorov complexity of the (non-)termination proof, and argue heuristically
that this gives our procedure various desirable qualities.
